% ======================================================================
%  Shared CV content. Style files define the semantic commands below,
%  then \input this file. Content is identical across all 5 variants.
%
%  Required commands (each style must define):
%   \makeheader
%   \cvsummary{text}
%   \cvsection{title}
%   \exprole{role}{org}{dates}{loc}{detail}
%   \eduentry{degree}{org}{dates}{loc}{detail}
%   \pubitem{tag}{authors}{title}{venuedetail}{url}{urltext}
%   \talkitem{tag}{text}
%   \skillline{label}{content}
%   \honoritem{name}{year}
%   \pubnote
% ======================================================================

\makeheader

\cvsummary{I work at the interface of \textbf{machine learning, computational chemistry, and experiment} to accelerate real-world materials discovery.}

% ---------------------------------------------------------------- Experience
\cvsection{Research Experience}
\exprole{Postdoctoral Researcher}{KAIST Graduate School of AI}{2026.03--Present}{Daejeon, Korea}{Advisor: Prof. Sungsoo Ahn}
\exprole{Graduate Student Researcher}{KAIST}{2020.02--2026.02}{Daejeon, Korea}{Advisor: Prof. Jihan Kim}
\exprole{Visiting Researcher}{Georgia Institute of Technology}{2023.04--2023.10}{Atlanta, GA}{Advisor: Prof. Andrew J. Medford}

% ---------------------------------------------------------------- Education
\cvsection{Education}
\eduentry{Ph.D., Chemical and Biomolecular Engineering}{KAIST}{2022.03--2026.02}{Daejeon, Korea}{Advisor: Prof. Jihan Kim.\\ Dissertation: \textit{Closing the Simulation--Experiment Gap in Metal--Organic Frameworks: Computational Methodology and Structural Data Reliability.}}
\eduentry{M.S., Chemical and Biomolecular Engineering}{KAIST}{2020.03--2022.02}{Daejeon, Korea}{Advisor: Prof. Jihan Kim.}
\eduentry{B.S., Chemical and Biomolecular Engineering}{KAIST}{2015.03--2020.02}{Daejeon, Korea}{Cum Laude.}
\eduentry{Exchange Student}{TU Dortmund}{2018.09--2019.02}{Dortmund, Germany}{}

% ---------------------------------------------------------------- Journal
\cvsection{Selected Publications}
% {venue}{year}{authors}{title}{vol}{url}{urltext}
\pubitem{Preprint}{2026}{Y. Kim, S. Kim, S. Ahn$^*$, \& \textbf{H. Kim}$^*$}{MADField: Multi-fidelity Amortized Density Field for Adsorption in Nanoporous Materials}{}{https://arxiv.org/abs/2606.21284}{arXiv:2606.21284}
\pubitem{Preprint}{2025}{\textbf{H. Kim}, D. Kim, \& J. Kim$^*$}{LitMOF: An LLM Multi-Agent for Literature-Validated Metal--Organic Frameworks Database Correction and Expansion}{}{https://arxiv.org/abs/2512.01693}{arXiv:2512.01693}
\pubitem{J. Phys. Chem. C}{2024}{\textbf{H. Kim}, N. K. Yu, N. Tian, \& A. J. Medford$^*$}{Assessing Exchange-Correlation Functionals for Heterogeneous Catalysis of Nitrogen Species}{}{https://pubs.acs.org/doi/full/10.1021/acs.jpcc.4c01497}{doi:10.1021/acs.jpcc.4c01497}
\pubitem{Adv. Mater.}{2024}{J. Park$^\dagger$, \textbf{H. Kim}$^\dagger$, S. Kim, S. Y. Yi, H. Min, D. Choi, S. Lee, J. Kim$^*$, \& J. Lee$^*$}{Boosting Alkaline Hydrogen Oxidation Activity of Ru Single-Atom through Promoting Hydroxyl Adsorption on Ru/WC$_{1-x}$ Interfaces}{}{https://advanced.onlinelibrary.wiley.com/doi/abs/10.1002/adma.202308899}{doi:10.1002/adma.202308899}
\pubitem{RSC Advances}{2022}{\textbf{H. Kim} \& J. Kim$^*$}{Theoretical Study of Induced Selective N$_2$ Binding under an Electric Field in MOF-74: Application for N$_2$/CH$_4$ Separations}{}{https://doi.org/10.1039/D2RA04216A}{doi:10.1039/D2RA04216A}

% ---------------------------------------------------------------- Full list
\cvsection{Full Publication List}
\cvsubsection{Journal Articles}
\fullpub{ACS Nano}{2025}{D. Jeon, H. Shin, J. H. Cha, \textbf{H. Kim}, S. Park, J. Ahn, S. H. Cho, C. Park, D. H. Kim, E. Shin, H. Baik, J. Kim, S. Y. Choi$^*$, \& I. D. Kim$^*$}{Photothermal Annealing-Enabled Millisecond Synthesis of Carbon Nanoonions and Simultaneous Single-Atom Functionalization}{}{https://pubs.acs.org/doi/full/10.1021/acsnano.5c11229}{doi:10.1021/acsnano.5c11229}
\fullpub{JACS Au}{2024}{J. Park, \textbf{H. Kim}, Y. Kang, Y. Lim, \& J. Kim$^*$}{From Data to Discovery: Recent Trends of Machine Learning in Metal--Organic Frameworks}{}{https://pubs.acs.org/doi/full/10.1021/jacsau.4c00618}{doi:10.1021/jacsau.4c00618}
\fullpub{J. Phys. Chem. C}{2024}{\textbf{H. Kim}, N. K. Yu, N. Tian, \& A. J. Medford$^*$}{Assessing Exchange-Correlation Functionals for Heterogeneous Catalysis of Nitrogen Species}{}{https://pubs.acs.org/doi/full/10.1021/acs.jpcc.4c01497}{doi:10.1021/acs.jpcc.4c01497}
\fullpub{Adv. Mater.}{2024}{J. Park$^\dagger$, \textbf{H. Kim}$^\dagger$, S. Kim, S. Y. Yi, H. Min, D. Choi, S. Lee, J. Kim$^*$, \& J. Lee$^*$}{Boosting Alkaline Hydrogen Oxidation Activity of Ru Single-Atom through Promoting Hydroxyl Adsorption on Ru/WC$_{1-x}$ Interfaces}{}{https://advanced.onlinelibrary.wiley.com/doi/abs/10.1002/adma.202308899}{doi:10.1002/adma.202308899}
\fullpub{ACS Sensors}{2023}{M. Jeon, M. Kim, J. S. Lee, \textbf{H. Kim}, S. J. Choi, H. R. Moon, \& J. Kim$^*$}{Computational Prediction of Stacking Mode in Conductive Two-Dimensional Metal--Organic Frameworks}{}{https://pubs.acs.org/doi/abs/10.1021/acssensors.3c00715}{doi:10.1021/acssensors.3c00715}
\fullpub{Adv. Funct. Mater.}{2023}{S. Park, S. H. Jeon, \textbf{H. Kim}, J. Philips, D. H. Oh, J. Ahn, M. Kim, C. Park, S. Hong, J. Kim, W. C. Jung, \& I. D. Kim$^*$}{Imparting Metal Oxides with High Sensitivity toward Light-Activated NO$_2$ Detection via Tailored Interfacial Chemistry}{}{https://advanced.onlinelibrary.wiley.com/doi/abs/10.1002/adfm.202214008}{doi:10.1002/adfm.202214008}
\fullpub{RSC Advances}{2022}{\textbf{H. Kim} \& J. Kim$^*$}{Theoretical Study of Induced Selective N$_2$ Binding under an Electric Field in MOF-74: Application for N$_2$/CH$_4$ Separations}{}{https://doi.org/10.1039/D2RA04216A}{doi:10.1039/D2RA04216A}

\cvsubsection{Conference Papers}
\fullpub{ICML}{2026}{S. Kim, C. Lee, Y. Kim, S. Yun, \textbf{H. Kim}, N. Kim, C. Park, S. Han, S. Lim$^*$, \& S. Ahn$^*$}{Machine Learning Hamiltonians are Accurate Energy-Force Predictors}{}{https://arxiv.org/abs/2602.16897}{arXiv:2602.16897}
\fullpub{ICML}{2026}{M. Kim, N. Kim, \textbf{H. Kim}, \& S. Ahn$^*$}{CatFlow: Co-generation of Slab-Adsorbate Systems via Flow Matching}{}{https://arxiv.org/abs/2602.05372}{arXiv:2602.05372}

\cvsubsection{Preprints}
\fullpub{}{2026}{Y. Kim, S. Kim, S. Ahn$^*$, \& \textbf{H. Kim}$^*$}{MADField: Multi-fidelity Amortized Density Field for Adsorption in Nanoporous Materials}{}{https://arxiv.org/abs/2606.21284}{arXiv:2606.21284}
\fullpub{}{2026}{N. Kim, \textbf{H. Kim}, S. Yu, M. Kim, S. Kim, \& S. Ahn$^*$}{AtomMOF: All-Atom Flow Matching for MOF-Adsorbate Structure Prediction}{}{https://arxiv.org/abs/2602.07351}{arXiv:2602.07351}
\fullpub{}{2026}{H. Jang, H. Seo, \textbf{H. Kim}, S. Park, T. Kim, Y. Jang, \& S. Ahn$^*$}{A Systematic Evaluation of Co-folding Model Representations for Small-Molecule Learning}{}{https://arxiv.org/abs/2602.13249}{arXiv:2602.13249}
\fullpub{}{2025}{\textbf{H. Kim}, D. Kim, \& J. Kim$^*$}{LitMOF: An LLM Multi-Agent for Literature-Validated Metal--Organic Frameworks Database Correction and Expansion}{}{https://arxiv.org/abs/2512.01693}{arXiv:2512.01693}

\pubnote

% ---------------------------------------------------------------- Presentations
\cvsection{Presentations}
\talkitem{Oral}{MRS Fall 2025, ``LLM-Driven Multi-Agent Curation and Expansion of Metal--Organic Frameworks Database''. Boston, MA. Dec 2025.}
\talkitem{Oral}{KIChE Fall Meeting and International Symposium, ``LLM-Driven Multi-Agent Curation and Expansion of Metal--Organic Frameworks Database''. Jeju, Korea. Oct 2025.}
\talkitem{Poster}{KIChE Fall Meeting and International Symposium, ``Induced Selective N$_2$ Binding under Electric Field: Application for the Separation of N$_2$/CH$_4$ and N$_2$/CO$_2$''. Gwangju, Korea. Oct 2021.}

% ---------------------------------------------------------------- Skills
\cvsection{Skills}
\skillline{Computational}{Python (PyTorch, LangGraph, LangChain), VASP (DFT), Gaussian (DFT), LAMMPS (MD), RASPA (GCMC)}
\skillline{Language}{English, Korean}

% ---------------------------------------------------------------- Honors
\cvsection{Honors \& Awards}
\honoritem{Mirae Asset Global Exchange Scholarship}{2018}
\honoritem{KAIST Support Scholarship}{2015 -- 2025}
